Modern Graph Generators: A Survey

### 2018-10-20 comparison.tex
Shrinking of the table
refactored community detection

               & \textbf{Target / sample}

@@

  &  &  &  &  &  &  &  &  &      \\

@@

  &  &  & &  &  &  & &  &      \\

@@

  &  &  & &  &  &  & &  &      \\

@@

\begin{table}
\scriptsize
\centering
\tbl{Overlapping of classes of generators} {
\begin{tabular}{| c | l | l | l | l | l | l | l | l | }
 \hline
           &  \textbf{Generator}
               & \textbf{\rot{General}}
               & \textbf{\rot{Semantic Web}}
               & \textbf{\rot{Graph databases\ }}
               & \textbf{\rot{Social networks}}
               & \textbf{\rot{Analytics}}
               & \textbf{\rot{Community detection}}
               & \textbf{\rot{Steaming}}
               \\ \hline
\hline   % ====================== general graphs
\multirow{5}{*}{\rot{\textbf{General}}}
  & Preferential attachment & {\bf x} & & & & x & & \\
\cline{2-9}
   & R-MAT    & {\bf x} & & & & x & & \\
\cline{2-9}
  & GraphGen  & {\bf x} & & x & & & & \\
\cline{2-9}
%  & Graph 500 & {\bf x} & & & & x & & \\
%\cline{2-9}
  & BTER      & {\bf x} & & & & & & \\
\cline{2-9}
  & Darwini   & {\bf x} & & & & & & \\
\hline
\hline %  ======================  Semantic web
\multirow{15}{*}{\rot{\textbf{Semantic web}}}
 & LUBM  & & {\bf x} & & & & & \\
\cline{2-9}
 & LBBM  & & {\bf x} & & & & & \\
\cline{2-9}
 & UOBM  & & {\bf x} & & & & & \\
\cline{2-9}
 & IIMB & & {\bf x} & & & & & \\
\cline{2-9}
 & BSBM & & {\bf x} & & & & & \\
\cline{2-9}
 & SP$^2$Bench & & {\bf x} & & & & & \\
\cline{2-9}
 & \cite{Duan:2011:AOC:1989323.1989340} & & {\bf x} & & & & & \\
\cline{2-9}
 & DBPSB & & {\bf x} & & & & & \\
\cline{2-9}
 & LODIB & & {\bf x} & & & & & \\
\cline{2-9}
 & SIB & & {\bf x} & & & & & \\
\cline{2-9}
 & Geographica & & {\bf x} & & & & & \\
\cline{2-9}
 & WatDiv & & {\bf x} & & & & & \\
\cline{2-9}
 & RBench & & {\bf x} & & & & & \\
\cline{2-9}
 & LDBC SPB & & {\bf x} & & & & & \\
\cline{2-9}
 & LinkGen & & {\bf x} & & & & & \\
\hline
\hline  % ======================  graph databases
\multirow{3}{*}{\rot{\textbf{GDBs}}}
  & XGDBench & & & {\bf x} & x & & & \\
\cline{2-9}
  & gMark & & x & {\bf x} & x & & & \\
\cline{2-9}
  & graphGen & & & {\bf x} & & & & \\
\hline
\hline %  ======================   social networks
\multirow{7}{*}{\rot{\textbf{SNs}}}
 & \cite{Barrett:2009:GAL:1995456.1995598} & & & & {\bf x} & & & \\
\cline{2-9}
 & \cite{Yao2011}  & & & & {\bf x} & & & \\
\cline{2-9}
 & LinkBench  & & & x & {\bf x} & & & \\
\cline{2-9}
 & S3G2  & & x & x & {\bf x} & & & \\
\cline{2-9}
 & \cite{Sukthankar-SocialInfo2014}  & & & & {\bf x} & & & \\
\cline{2-9}
 & LDBC SNB   & & x & x & {\bf x} & & & \\
\cline{2-9}
  & \cite{Nettleton2016}  & & & & {\bf x} & & & \\
\hline
\hline   % ======================   graph analytics
\multirow{1}{*}{\rot{\textbf{A}}}
  & HPC Scal. Graph Anal.  & & & & & {\bf x} & & \\
%\cline{2-9}
%  & Graphalytics & & & & & {\bf x} & & \\
\hline
\hline   %  ======================  community detection
\multirow{3}{*}{\rot{\textbf{Co}}}
  &  & & & & & & {\bf x} &\\
\cline{2-9}
  &  & & & & & & {\bf x} & \\
\cline{2-9}
  &  & & & & & & {\bf x} & \\
%\cline{2-9}
%  & & & & & & \\
\hline
\hline   %  ======================  streaming
\multirow{2}{*}{\rot{\textbf{St}}}
  & S2Gen & & & & & & & {\bf x}\\
\cline{2-9}
  & RSPLab & & & & & & & {\bf x} \\
%\cline{2-9}
%  & & & & & & & \\
\hline
\end{tabular} }
\label{tab:overlapping}
\end{table}

@@

>>>>

               & \textbf{Target/sample}

@@

  & Danon et al. & -- & -- & Y & N & N & uniform & edge-list &  N    \\

@@

  & LFR & -- & -- & Y & N & N & power-law & edge-list  & N      \\

@@

  & LFR-Overlapping & -- & -- & Y & N & N & power-law & edge-list & N     \\

@@

\begin{table}
\scriptsize
\centering
\tbl{Overlapping of classes of generators} {
\begin{tabular}{| c | l | l | l | l | l | l | l | l | }
 \hline
           &  \textbf{Generator}
               & \textbf{\rot{General}}
               & \textbf{\rot{Semantic Web}}
               & \textbf{\rot{Graph databases\ }}
               & \textbf{\rot{Social networks}}
               & \textbf{\rot{Analytics}}
               & \textbf{\rot{Community detection}}
               & \textbf{\rot{Steaming}}
               \\ \hline
\hline   % ====================== general graphs
\multirow{5}{*}{\rot{\textbf{General}}}
  & Preferential attachment & {\bf x} & & & & x & & \\
\cline{2-9}
   & R-MAT    & {\bf x} & & & & x & & \\
\cline{2-9}
  & GraphGen  & {\bf x} & & x & & & & \\
\cline{2-9}
%  & Graph 500 & {\bf x} & & & & x & & \\
%\cline{2-9}
  & BTER      & {\bf x} & & & & & & \\
\cline{2-9}
  & Darwini   & {\bf x} & & & & & & \\
\hline
\hline %  ======================  Semantic web
\multirow{15}{*}{\rot{\textbf{Semantic web}}}
 & LUBM  & & {\bf x} & & & & & \\
\cline{2-9}
 & LBBM  & & {\bf x} & & & & & \\
\cline{2-9}
 & UOBM  & & {\bf x} & & & & & \\
\cline{2-9}
 & IIMB & & {\bf x} & & & & & \\
\cline{2-9}
 & BSBM & & {\bf x} & & & & & \\
\cline{2-9}
 & SP$^2$Bench & & {\bf x} & & & & & \\
\cline{2-9}
 & \cite{Duan:2011:AOC:1989323.1989340} & & {\bf x} & & & & & \\
\cline{2-9}
 & DBPSB & & {\bf x} & & & & & \\
\cline{2-9}
 & LODIB & & {\bf x} & & & & & \\
\cline{2-9}
 & SIB & & {\bf x} & & & & & \\
\cline{2-9}
 & Geographica & & {\bf x} & & & & & \\
\cline{2-9}
 & WatDiv & & {\bf x} & & & & & \\
\cline{2-9}
 & RBench & & {\bf x} & & & & & \\
\cline{2-9}
 & LDBC SPB & & {\bf x} & & & & & \\
\cline{2-9}
 & LinkGen & & {\bf x} & & & & & \\
\hline
\hline  % ======================  graph databases
\multirow{3}{*}{\rot{\textbf{GDBs}}}
  & XGDBench & & & {\bf x} & x & & & \\
\cline{2-9}
  & gMark & & x & {\bf x} & x & & & \\
\cline{2-9}
  & graphGen & & & {\bf x} & & & & \\
\hline
\hline %  ======================   social networks
\multirow{7}{*}{\rot{\textbf{SNs}}}
 & \cite{Barrett:2009:GAL:1995456.1995598} & & & & {\bf x} & & & \\
\cline{2-9}
 & \cite{Yao2011}  & & & & {\bf x} & & & \\
\cline{2-9}
 & LinkBench  & & & x & {\bf x} & & & \\
\cline{2-9}
 & S3G2  & & x & x & {\bf x} & & & \\
\cline{2-9}
 & \cite{Sukthankar-SocialInfo2014}  & & & & {\bf x} & & & \\
\cline{2-9}
 & LDBC SNB   & & x & x & {\bf x} & & & \\
\cline{2-9}
  & \cite{Nettleton2016}  & & & & {\bf x} & & & \\
\hline
\hline   % ======================   graph analytics
\multirow{1}{*}{\rot{\textbf{A}}}
  & HPC Scal. Graph Anal.  & & & & & {\bf x} & & \\
%\cline{2-9}
%  & Graphalytics & & & & & {\bf x} & & \\
\hline
\hline   %  ======================  community detection
\multirow{3}{*}{\rot{\textbf{Co}}}
  & Danon et al. & x & & & & x & {\bf x} &\\
\cline{2-9}
  & LFR & x & & & & x & {\bf x} & \\
\cline{2-9}
  & LFR-Overlapping & x & & & & x & {\bf x} & \\
%\cline{2-9}
%  & & & & & & \\
\hline
\hline   %  ======================  streaming
\multirow{2}{*}{\rot{\textbf{St}}}
  & S2Gen & & & & & & & {\bf x}\\
\cline{2-9}
  & RSPLab & & & & & & & {\bf x} \\
%\cline{2-9}
%  & & & & & & & \\
\hline
\end{tabular} }
\label{tab:overlapping}
\end{table}

@@

Generators for community detection aim, in general, at creating graphs with a
more realistic strcture (graphs with communities of nodes where the density of
edges is larger internally than externally). Even though these generators are,
in general used to test community detection algorithms (they generate also the
expected communities in the graph), some studies also use them for general graph
purposes or to test graph analytics algorithms besides community detection.

### 2018-10-20 generators_community_detection.tex
Modification of tables (community detection)
refactored community detection

\subsubsection{Community Detection}
\label{sec:generators_community_detection}

@@

The first attempts to compare community detection algorithms using synthetic graphs proposed the use of random graphs composed by several Erd\"{o}s-R\'{e}nyi subgraphs, connected more internally than externally~\cite{danon2005comparing}. Each of these subgraphs has the same size and the same internal/external density of edges. However, such graphs miss the realism observed in real graphs, where communities are of different sizes and densities. Thus, Lancichinetti, Fortunato and Radicchi (hence LFR)~\cite{PhysRevE.78.046110} propose a class of benchmark graphs for community detection where communities are of different sizes and densities. The generator generates communities of different sizes following a power-law distribution whose parameters can be configured. The degree of the nodes is also sampled from a power-law distribution. Additionally, the generator introduces the concept of the ``mixing factor'', which specifies the fraction of its links connecting nodes belonging to different communities. Such parameter allows  the degree of modularity of the generated graph  to be tuned, thus testing the robustness of the algorithms under different conditions. The generation process starts with an empty graph and incrementally fills in the adjacency matrix by obeying the described constraints. Lancichinetti, Fortunato and Radicchi~\cite{PhysRevE.80.016118} extended LFR to support the notion of directed graphs and overlapping communities. Overlapping communities extend the notion of communities by allowing the sharing of vertices, thus a vertex can belong to more than one community. This extended generator allows controlling the same parameters of the previous version, but also the amount of overlap of the generated communities.

>>>>

\subsection{Community Detection}
\label{sec:generators_community_detection}

@@

\paragraph{Danon et al.} The first attempts to compare community detection algorithms using synthetic
graphs proposed the use of random graphs composed by several Erd\"{o}s-R\'{e}nyi
subgraphs, connected more internally than externally~\cite{danon2005comparing}.
Each of these subgraphs has the same size and the same internal/external density
of edges. However, such graphs miss the realism observed in real graphs, where
communities are of different sizes and densities, thus several proposals exist
to overcome such an issue.

\paragraph{LFR} Lancichinetti, Fortunato
and Radicchi (hence LFR)~\cite{PhysRevE.78.046110} propose a class of benchmark
graphs for community detection where communities are of different sizes and
densities. The generator generates communities of different sizes following a
power-law distribution whose parameters can be configured. The degree of the
nodes is also sampled from a power-law distribution. Additionally, the generator
introduces the concept of the ``mixing factor'', which specifies the fraction of
its links connecting nodes belonging to different communities. Such parameter
allows  the degree of modularity of the generated graph  to be tuned, thus
testing the robustness of the algorithms under different conditions. The
generation process starts with an empty graph and incrementally fills in the
adjacency matrix by obeying the described constraints.

\paragraph{LFR-Overlapping} Lancichinetti, Fortunato and
Radicchi~\cite{PhysRevE.80.016118} extended LFR to support the notion of
directed graphs and overlapping communities. Overlapping communities extend the
notion of communities by allowing the sharing of vertices, thus a vertex can
belong to more than one community. This extended generator allows controlling
the same parameters of LFR, as well as the amount of overlap of
the generated communities.
